A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-04 ms.Rmd
a few formatting things and some discussion started.

---
title: "A continuous urbanization index to assess phylogenetic adaptations in urban bird living"
author: Corey T. Callaghan, John Wilshire, XXXX, XXXX, Richard T. Kingsford, William K. Cornwell
date: ""
output:
  pdf_document: null
  bookdown::word_document2: null
  bookdown::tufte_html2:
    number_sections: no
    toc: no
  html_document:
    df_print: paged
    toc: no
fontsize: 12pt
link-citations: no
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/global-ecology-and-biogeography.csl
bibliography: references.bib
---

@@

https://www.youtube.com/watch?v=9Gc4QTqslN4

@@

### Non-phylogenetically constrained models
Given that we hypothesized any of the potential candidate traits could significantly drive the response in our urbanization index, we first ran one global model including all 22 explanatory variables. We then used the standardize function from the arm package [@gelman2008scaling; @gelman2016arm] to standardize model estimates to represent relative effect sizes. In order to confirm our linear model results, we employed a model-averaging approach [@grueber2011multimodel] in which we 'dredged' possible subsets of the global model. This was done using the dredge function in the MuMIn package [@barton2016mumin], and we allowed a total of 11 candidate predictors to be fit at any one time in order to avoid over-fitting. This left a total of 784,626 models which were assessed, and the model-averaged parameter estimates were calculated from the top models of those with ∆AIC < 4. As with the global model, we present the standardized estimates which represent relative effect sizes

@@

# DISCUSSION

>>>>

---
title: "A continuous urbanization index to assess phylogenetic adaptations in urban bird living"

author: | 
  | Corey T. Callaghan^[Corresponding author: c.callaghan@unsw.edu.au] $^1$, Richard E. Major $^1$$^,$$^2$, John H. Wilshire $^1$, John M. Martin $^1$$^,$$^3$, Richard T. Kingsford $^1$, William K. Cornwell $^1$$^,$$^4$
  | $^1$Center for Ecosystem Science, School of Biological, Earth and Environmental Sciences, UNSW Sydney, Sydney, NSW, Australia; $^2$Australian Museum Research Institute, Sydney, NSW, Australia; $^3$Royal Botanic Gardens and Domain Trust, Sydney, NSW, Australia; $^4$Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Sciences, UNSW Sydney, Sydney, NSW, Australia
date: ""
output:
  pdf_document: null
  bookdown::word_document2: null
  bookdown::tufte_html2:
    number_sections: no
    toc: no
  html_document:
    df_print: paged
    toc: no
fontsize: 12pt
link-citations: no
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology-letters.csl
bibliography: references.bib
header-includes: 
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---

\newpage

@@

TBD

@@

### Non-phylogenetically constrained models
Given that we hypothesized any of the potential candidate traits could significantly drive the response in our urbanization index, we first ran one global model including all 22 explanatory variables. We then used the standardize function from the arm package [@gelman2008scaling; @gelman2016arm] to standardize model estimates to represent relative effect sizes. In order to confirm our linear model results, we employed a model-averaging approach [@grueber2011multimodel] in which we 'dredged' possible subsets of the global model. This was done using the dredge function in the MuMIn package [@barton2016mumin], and we allowed a total of 11 candidate predictors to be fit at any one time in order to avoid over-fitting. This left a total of 784,626 models which were assessed, and the model-averaged parameter estimates were calculated from the top models of those with ???AIC < 4. As with the global model, we present the standardized estimates which represent relative effect sizes

@@

# DISCUSSION
We found a significant effect of phylogenetic signal in our study, which contrasts with previous studies [@evans2011makes]. Niche breadth, as measured by generalism, was significantly associated with our urbanization index across all analyses. Conversely, granivores and insectivores were consistently selected against. Residual brain mass was significantly important within our phylogenetic models, suggesting that within a clade, it is the species with the largest residual brain mass that are most readily observed in urban areas. A similar pattern was found for body size, although not significant. Our results suggests that urbanization selects against specialist species.

Generalists are ultimately better prepared to thrive, survive, and adapt within urban areas.

We provide the largest study to date using a continuous urbanization metric in order to assess biological and ecological traits which predict a species' adaptability to urban environments. Understanding specific species' traits which are associated with urban birds allows us to fully understand how to best preserve and maintain avian diversity in cities. We recommend that urban areas should focus on providing habitats which allow granivores, insectivores, and others to be found more readily in cities.
